Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-15 paper/paper.tex
More precise lemma 1req formulation

In our analysis, we distinguish among three types of clusters, $C_1, C_2, C_3$. In cluster of type $C_i$, the size of the largest component contained in this cluster is $i$.

\begin{lemma}
  \label{lem:1req}
  A single repartition performed by \TAlg{} incurs the cost at most $3\cdot\alpha$.
\end{lemma}

@@

  Before we bound the competitive ratio, we relate the costs of $\TAlg$ and $\OPT$ with respect to $\sigma_E$.
  We begin by lower-bounding the number of requests from $\sigma_E$ that $\OPT$ must account (by either serving remotely or migrating), and we denote their number by $x$.
  It holds that $x \geq \TAlg(\sigma_E) - 3\cdot\ell\cdot(\alpha - 1)$, as it received all the requests that \TAlg did, but it could ignore the cost of serving at most $3\cdot\ell$ pairs of nodes, as it might have them collocated in its clusters.
  Each such pair of nodes account for at most $\alpha-1$ requests (the pairs from $\sigma_E$ are unsaturated) in the cost of $\TAlg(\sigma_E)$, hence collocating them would decrease the number by at most $3\cdot\ell\cdot(\alpha - 1)$.

@@

\end{appendix}

>>>>

In our analysis, we distinguish among three types of clusters: $C_1, C_2, C_3$. In a cluster of type $C_i$, the size of the largest component contained in this cluster is $i$.

\begin{lemma}
  \label{lem:1req}
  The cost of migrations during a single repartition of \TAlg is at most $3\cdot\alpha$.
\end{lemma}

@@

  \medskip
  Before we bound the competitive ratio, we relate the costs of $\TAlg$ and $\OPT$ with respect to $\sigma_E$.
  We begin by lower-bounding the number of requests from $\sigma_E$ that $\OPT$ must account (by either serving remotely or migrating), and we denote their number by $x$.
  It holds that $x \geq \TAlg(\sigma_E) - 3\cdot\ell\cdot(\alpha - 1)$, as it received all the requests that \TAlg did, but it could ignore the cost of serving at most $3\cdot\ell$ pairs of nodes, as it might have them collocated in its clusters.
  Each such pair of nodes account for at most $\alpha-1$ requests (the pairs from $\sigma_E$ are unsaturated) in the cost of $\TAlg(\sigma_E)$, hence collocating them would decrease the number by at most $3\cdot\ell\cdot(\alpha - 1)$.

@@

\todo{Line endings (add tildes where necessary)}
\end{appendix}
